%-------------------------
% Resume in Latex
% Author : Almaz Nurman
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/al-nurman}{\Large Almaz Nurman}} & Email : \href{mailto:almazbrr@gmail.com}{almazbrr@gmail.com}\\
  \href{https://www.linkedin.com/in/al-nurman}{https://www.linkedin.com/in/al-nurman} & Mobile : \href{tel:+19804088111}{+1-980-408-8111} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Astrakhan State Technical University}{Astrakhan, Russia}
      {Master of Science in Computer Science;  GPA: 3.9}{Sep. 2000 - Jul. 2005}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Shift Startup}{Charlotte, NC}
      {Senior Software Engineer}{May 2023 - Present}
      \resumeItemListStart
        \resumeItem{Shift Mobile}{Designed and created a mobile application for technicians, enabling device inventory management, financial report generation, device reconciliations, team communication, and location tracking.}
      \resumeItemListEnd
      
    %\resumeSubheading{Epam Systems}{Remote}{Senior Software Engineer}{Sep. 2022 - Apr. 2023}\resumeItemListStart\resumeItem{Epam Anywhere}{Overloaded hiring web application. Involved in features such as bug tracking, queuing and A/B testing. Built an micro-service for an article publishing.}\resumeItemListEnd
    
    \resumeSubheading{DAR Tech}{Almaty, Kazakhstan}{Senior Backend Developer}{Sep. 2022 - Apr. 2023}\resumeItemListStart\resumeItem{DOSSYM}{Constructed a Restful API for a financial web application that facilitated the posting of transactions in the Accounting system.}\resumeItem{HRM}{Created a Restful API for a Payroll application, facilitating the migration of time-sheets from the management system.}\resumeItemListEnd

    \resumeSubheading{FirstBit Middle East}{Dubai, UAE}{Implementation Project Manager}{May 2021 - Sep. 2022}\resumeItemListStart\resumeItem{JamalCo}{Spearheaded the ERP implementation project for a construction company, tailoring calculations for the breakdown of road marking projects.}\resumeItem{Goldman}{Led the ERP implementation project for a real estate company, customizing the documentation process.}\resumeItemListEnd
    
    \resumeSubheading{Borusan CAT}{Almaty, Kazakhstan}{Senior Software Engineer}{Mar. 2014 - Dec. 2021}
    \resumeItemListStart
    
        \resumeItem{Optimization customized ERP}{Substantially enhanced MS SQL database performance through the implementation and optimization of SQL queries and stored procedures. Additionally, transformed data blocking from tables wide to row wide using filters specific to each table column during the rebuild process. These measures collectively led to a remarkable 34\% improvement in the overall system performance.}
        \resumeItem{WH Balykchy}{Inventory Management System for Caterpillar's workshop in Balykchy, Kyrgyzstan. Implemented MS SQL Database according standard of Caterpillar data structure. }
        \resumeItem{Integration with Caterpillar API}{Designed and implemented integration's with Caterpillar web services, utilizing SOAP XML and RESTful API with JSON, encompassing Invoicing Service, NPR, Price Service, Debit Note Service, and Part Availability Service across three dealership CAT locations.}
        \resumeItem{Integration with TBC Bank}{Designed and developed seamless integration's with the TBC bank web application.}
    \resumeItemListEnd

    \resumeSubheading{TopLine}{Almaty, Kazakhstan}{Software Developer}{Jan. 2010 - Feb. 2014}\resumeItemListStart\resumeItem{Mobile Trade}{Engineered a mobile application tailored for VAN sales and PRE sales, catering specifically to the needs of retail companies.}\resumeItem{SPA ERP}{Crafted and developed a specialized ERP system for SPA centers, incorporating optimized data structures and establishing seamless integration's with the Accounting module.}\resumeItemListEnd
      
    \resumeSubheading{Astrakhan State Technical University}{Astrakhan, Russia}{Software Developer}{Jun. 2004 - Jul. 2005}\resumeItemListStart\resumeItem{Schedule generator - Game theory}{Conducted research on machine learning to address the challenge of generating class schedules at a university. Applied algorithms on graphs with weighted edges, and subsequently developed a C++ application.}\resumeItem{Science Article}{scientific article on the application of game theory in solving the problem of generating a class schedule at a university. Published in university scientific publication "Science and Investigations 2005"}\resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{Shift Mobile}{Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mobile Trade}{Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{SPA ERP}{Crafted and developed a specialized ERP system for SPA centers, incorporating optimized data structures and establishing seamless integrations with the Accounting module.}
%  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Kotlin, JavaScript, C\#, Java, SQL}
      \hfill
      \textbf{Technologies}{: AWS, Firebase, React, Kafka, Android}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
